Constructing the transition graphs of interacting hysterons

### 2022-07-05 Paper_draft.tex
Added explanation for building up a transition graph & image for initation/stability conditions

@@

We observe that in essence, it is only the ordering of the switching fields ${U_i^{+, -}(S)}$ that determines the state transition graph, rather than their absolute value. As a result, there can only be as many graphs as there are permutations of the order of switching fields. In the case where hysterons are non-interacting, there are only $2N$ switching fields $\{u_i^{+, -}\}$. In addition, because we never compare an up switching field with a down switching fields in the absence of avalanches, the only orderings that can change the graph are the partial orderings of the up switching fields $\{u_i^+\}$ and of the down switching fields $\{u_i^-\}$. The number of orderings that can lead to a unique graph is then $N!\times N!$. When we fix the up switching fields to account for exchange symmetry, we find that the number of permutations is only $N!$.\\

>>>>

    \includegraphics[width=0.5\textwidth]{initstability.pdf}
    \caption{Linear inequalities imposed by initiation \& stability conditions of an example transition.}
    \label{fig:initstability}

@@

The possible transitions from a stable state $S$ of the system are found in two steps. First, we vary the external driving $U$ until it reaches a value where a hysteron flips, which we will call $U^*$. There are two possible transitions at each state, corresponding to an increase or decrease in the driving $U$. For an increase in the driving $U$, the first hysteron to flip is that with the lowest up switching field, which we denote as $U^+(S)$:
\begin{equation}\label{eq:globalup}
U^* = U^+(S) = \min_{s_j = 0}U_j^+(S)
For a decrease in the driving $U$, the first hysteron to flip is that with the highest down switching field, which we call $U^-(S)$:
\begin{equation}\label{eq:globaldown}
U^* = U^-(S) = \max_{s_j = 1}U_j^+(S)
\end{equation}\\
After a hysteron is flipped, we let the system relax by holding the driving at $U^*$ until a new stable state is reached. Stability under the field $U^*$ means that all hysterons in phase $s_i=0$ have up switching fields higher than $U^*$, while all hysterons in phase $s_i = 1$ have down switching fields lower than $U^*$. By applying the two steps of initiation and stability to all stable states, we find the entire transition graph. \\
We now consider how the values of the switching fields can influence the transition graph at each of the two steps. For the iniation, we only compare up switching fields with up switching fields, and down switching fields with down switching fields, at the same state $S$. At the second step, we compare both up switching fields and down switching fields with the current value of the driving, which is the field $U^*$ which initiates a transition. However, $U^*$ itself given by Equations \ref{eq:globalup} and \ref{eq:globaldown}, and thus equal to one of the switching fields $U_i^{+, -}(S)$. We remark that for both steps the transition graph only depends on a set of linear inequalities $U_i(S_A) > U_j(S_B)$. It follows that the transition graph is purely determined by the order of switching fields, rather than their absolute value.\\
In the case where hysterons are non-interacting, there are only $2N$ switching fields $\{u_i^{+, -}\}$. In addition, because we never compare an up switching field with a down switching fields in the absence of avalanches, the only orderings that can change the graph are the partial orderings of the up switching fields $\{u_i^+\}$ and of the down switching fields $\{u_i^-\}$. The number of orderings that can lead to a unique graph is then $N!\times N!$. When we fix the up switching fields to account for exchange symmetry, we find that the number of permutations is only $N!$.\\
